---
title: "LabJournal3"
author: "Keiichiro Watanabe"
date: "2023-09-11"
output: pdf_document
editor_options: 
  markdown: 
    wrap: sentence
---

# Part 1: Visualizing Data in R

## 1

```{r}
library(magrittr)
# Create a simple data frame
df <- data.frame(a = 1:5, b = 6:10)
# Using %$% to directly refer to columns a and b
result <- df %$% {
  c(mean(a), mean(b))
}
print(result)
```

## 4

```{r}
library(qrcode)

# Generate QR code for a personal website
qr_code_website <- qr_code("https://keiichiro1101.github.io/")

# Save QR code as a PNG image
png("personal_website_qr.png")
plot(qr_code_website)
dev.off()
```

```{r}
# Generate QR code for linkedin
qr_code_linkedin <- qr_code("www.linkedin.com/in/keiichiro-watanabe-b1949526b")

# Save QR code as a PNG image with a different name
png("linkedin_qr.png")
# Plot with custom colors
plot(qr_code_linkedin, col = c("blue", "yellow"))
dev.off()
```

## 5

```{r}
# Generate random data
data <- rnorm(1000, mean = 50, sd = 10)

# Plot histogram using Base R
hist(data, main = "Histogram using Base R", xlab = "Value", ylab = "Frequency", col = "lightblue", border = "black")
```

```{r}
library(ggplot2)

# Create a data frame
data_df <- data.frame(Value = data)

# Plot histogram using ggplot2
ggplot(data_df, aes(x = Value)) +
  geom_histogram(binwidth = 1, fill = "blue", alpha = 0.7) +
  ggtitle("Histogram using ggplot2") +
  xlab("Value") +
  ylab("Frequency")
```

```{r}
library(lattice)
# Plot histogram using histogram function from lattice
histogram(~data, main = "Histogram using lattice", xlab = "Value", ylab = "Frequency", col = "gray")
```

## 6

### 1

Variables: These include url, timedelta, n_tokens_title, n_tokens_content, n_unique_tokens, num_hrefs, num_self_hrefs, num_imgs, etc.

Observations: Each row in the data frame is an observation, describing various characteristics of a single article, such as its URL, how many tokens are in the title and content, the number of images, etc.

Values: Values are the individual data points in the cells of the data frame.
For example, in the first row, the value of timedelta is 731, and the value of n_tokens_title is 12.

### 2

#### What is Pivoting?

Pivoting is a way to reshape the data; you might convert data from a "long" format to a "wide" format or vice versa.
This can be done using functions like pivot_longer() and pivot_wider() in R.

#### When is Pivoting Useful?

Data Analysis: Pivoting can help rearrange data in a way that makes it easier to analyze.

Data Visualization: Pivoting helps make data more compatible for various types of graphs.
For example, a longer format could be more suitable for line plots.

Data Aggregation: When wanting to summarize data, the shape of the data can make a difference.
Sometimes, it's easier to aggregate data in a long format, while other times a wide format is more convenient.

Example of Pivoting

```{r}
library(tidyverse)

my_data <- read.csv("/Users/keiichiro_watanabe/Desktop/CSC324/IndividualProject/data/OnlineNewsPopularity.csv")

# Convert to longer format
my_data_long <- my_data %>%
  pivot_longer(cols = starts_with("data_channel_is_"), names_to = "Data_Channel", values_to = "Is_Channel_Active")

# Now, group by the data channel and summarize
my_data_summary <- my_data_long %>%
  filter(Is_Channel_Active == 1) %>%
  group_by(Data_Channel) %>%
  summarize(Avg_Shares = mean(shares, na.rm = TRUE))
```

## 7

### 1

The diagram illustrates the relationships between various tables (airlines, airports, planes, and weather) in the nycflights13.
The diagram serves to illustrate how these tables are related to the central flights table.
In a relational database, this setup would facilitate complex queries across multiple tables, allowing us to gather detailed information for any given flight easily.

### 2

#### Primary Keys

A primary key is a column (or set of columns) in a table whose values uniquely identify each row in that table.
The primary key must contain unique values, and it cannot contain NULL values.
A table can have only one primary key, which may consist of single or multiple columns.
For example, tailnum could be a primary key for the planes table, carrier could be a primary key for the airlines table, and faa could be a primary key for the airports table.

#### Foreign Keys

A foreign key is a column (or set of columns) in one table that serves as a reference to the primary key in another table.
The table that contains the foreign key is called the "referencing" or "child" table, and the table being referred to by the foreign key is the "referenced" or "parent" table.
Foreign keys enforce referential integrity, ensuring that the relationship between tables remains consistent.
In the flights table, the columns tailnum, carrier, origin, and dest are foreign keys connecting to the primary keys in the planes, airlines, and airports tables, respectively.

## 8

### Key Variables:

Article Popularity: Measured by the number of social media shares.

Content: Various metrics about the content of the articles such as 'n_tokens_title', 'n_tokens_content', etc.

Timing: Features like 'timedelta', which could represent the time since the article was published.

Sentiment: Metrics like 'global_sentiment_polarity', 'rate_positive_words', etc., that might capture the sentiment of the article.

### What the Scatterplot Matrix Could Reveal:

Correlation with Popularity: we can identify which variables have the strongest correlation with the number of shares.
For example, articles with a higher 'global_sentiment_polarity' might be shared more often.

Content-Length vs. Shares: scatterplot between 'n_tokens_content' (article length) and 'shares' might reveal if longer articles are more popular or if there's a sweet spot in article length that maximizes shares.

Timing and Popularity: plotting 'timedelta' against 'shares', could explore whether articles gain more shares as they age or if newer articles tend to be more popular.

Sentiment and Popularity: sentiment variables like 'global_sentiment_polarity' or 'rate_positive_words' might show how the emotional tone of an article influences its likelihood of being shared.

```{r}
# Select specific columns for the scatterplot matrix
selected_columns <- my_data[, c("shares", "n_tokens_title", "n_tokens_content", "timedelta", "global_sentiment_polarity")]

# Generate the scatterplot matrix
plot(selected_columns)

```

## 9

Word clouds are visual representations of text data where the frequency of each word is represented by its size in the cloud.
The more frequently a particular word appears in a text, the larger and bolder it appears in the word cloud.

Word clouds are often used for: Data Visualization: They can give a quick overview of the most prominent terms in a large corpus of text.
SEO Analysis: They can be used to summarize key terms that should be included on a webpage.
Text Mining: They can serve as a starting point for more detailed text mining efforts.

Limitations: Lack of Context: They show words without context, so synonymous terms or phrases that mean the same thing can appear separately.
Not Quantitative: The size difference between words doesn't convey precise numerical differences in frequency.

```{r}
library(wordcloud)

# Sample text data
text <- c("Data", "Science", "R", "Python", "Machine", "Learning", "Statistics", "Data", "Visualization")

# Create word cloud
wordcloud(text, min.freq = 1, random.order = FALSE)
```

# Part 2: Reflection and questions on readings

## 1

Perspective distortion has the capabilities to take away from the greater data set by altering the overall meaning that the user can derive from the data.
Sometimes a three dimensional rendering can take away from the user's understanding due to the complex nature of the figures given.
Contour plots are incredibly useful for both two dimensional and three dimensional of data renderings.

## 2

### 1. Timing and Popularity

What: Analyze the relationship between the age of Mashable articles ('timedelta') and their popularity ('shares').

Why: To discover if articles gain more shares as they age or if newer articles tend to be more popular.

How: A scatterplot where the X-axis represents the age of the article and the Y-axis represents the number of shares.
Each point is an article.
Findings:

If the plot shows an upward trend, it could mean that articles gain more shares as they age.
A downward trend could imply that newer articles are more popular.
No pattern may indicate that timing is not a strong factor in an article's popularity.

### 2. Sentiment and Popularity

What: Examine the relationship between sentiment variables ('global_sentiment_polarity', 'rate_positive_words') and the popularity of Mashable articles ('shares').

Why: To determine how the emotional tone of an article influences its likelihood of being shared.

How: A scatterplot where the X-axis could represent 'global_sentiment_polarity' or 'rate_positive_words' and the Y-axis represents the number of shares.
Each point is an article.
Findings:

If the points cluster towards the top right, it might indicate that articles with a more positive tone get more shares.
If points cluster towards the top left, it could mean that articles with a more negative tone are more popular.
No pattern might suggest that sentiment does not significantly affect an article's popularity.

# Reference

Name(s) of all authors: Keiichiro Watanabe, Megan Bernacchi

Lab: Lab Journal 2

Due Monday, 11 September 2023

Written/online sources used: (enter "none" if no sources other than the textbook and course website used) : none

Help obtained (Acknowledgments): none

"I/we confirm that the above list of sources is complete AND that I/we have not talked to anyone else about the solution to this problem."
