---
title: "labJournal2"
author: "Keiichiro Watanabe"
date: "2023-09-04"
output: pdf_document
editor_options: 
  markdown: 
    wrap: 72
---
# Part 0: Let’s discuss the previous lab.
R has a unique ecosystem called Tidyverse that simplifies data manipulation and visualization, making it easier to work with data in a "tidy" format.

RStudio isn't just an IDE; it's a comprehensive toolkit for data science, featuring Git integration, R Markdown support, and much more.

R excels at vectorized operations, allowing for efficient data manipulation without explicit loops, which speeds up data analysis.

# Part 1: Data Manipulation in R

## 1

getwd() : returns the current working directory in a string.

setwd(): set the current working environment.

## 2

Tibbles is a formatting tool.

## 3

The %\<\>% operator is often referred to as the compound assignment
pipe-operator and comes from the magrittr package in R

```{r}
library(magrittr)

x <- c(1, 2, 3, 4, 5)

# Use %<>% to square the values and then subtract 1
x %<>% (function(y) y^2) %>% subtract(1)

print(x)

```

## 4

The str function in R is used for compactly displaying the internal
structure of an R object. This function provides a quick and convenient
way to get an overview of the data types, dimensions, and contents of
lists, vectors, matrices, data frames, and more.

Type of Object: Tells you whether it's a vector, list, data frame, etc.

Dimensions: For matrices and data frames, it shows the number of rows
and columns.

Content: A preview of the actual data contained within the object.

Attributes: Any additional attributes that the object might have.

## 5

### 1

```{r}
my_data <- read.csv("/Users/keiichiro_watanabe/Desktop/CSC324/IndividualProject/data/OnlineNewsPopularity.csv")
```

### 2

Mutate
```{r}
library(dplyr)
# Adding a new column "content_ratio" that is the ratio of n_tokens_content to n_tokens_title
my_data <- my_data %>%
  mutate(content_ratio = n_tokens_content / n_tokens_title)
```

Summarize
```{r}
# Summarizing to find the average number of tokens in the content
summary_result <- my_data %>%
  summarize(avg_n_tokens_content = mean(n_tokens_content))
```

Arrange
```{r}
# Sorting the data by the number of shares, in descending order
my_data_sorted <- my_data %>%
  arrange(desc(shares))
```

Filter
```{r}
# Filtering rows where data_channel_is_tech is 1.
my_data_tech <- my_data %>%
  filter(data_channel_is_tech == 1)

# Filtering rows where the number of shares is greater than 1000.
my_data_high_shares <- my_data %>%
  filter(shares > 1000)

# Filtering rows where the article was posted on a weekend.
my_data_weekend <- my_data %>%
  filter(is_weekend == 1)

```

Select
```{r}
# Selecting columns related to token counts
# -----------------------------------------------------
my_data_tokens <- my_data %>%
  select(n_tokens_title, n_tokens_content)
# -----------------------------------------------------

# Selecting columns related to data channels
# -----------------------------------------------------
my_data_channels <- my_data %>%
  select(starts_with("data_channel"))
# -----------------------------------------------------

# Selecting columns related to weekdays
# -----------------------------------------------------
my_data_weekdays <- my_data %>%
  select(weekday_is_monday:weekday_is_sunday)
# -----------------------------------------------------

# Selecting columns where the average token length is greater than 4
# -----------------------------------------------------------------------------
my_data_avg_token_length <- my_data %>%
  select(average_token_length) %>%
  filter(average_token_length > 4)
# -----------------------------------------------------------------------------

# Selecting columns with logical conditions on n_unique_tokens and n_non_stop_unique_tokens
# ----------------------------------------------------------------------------------------------------
my_data_logical <- my_data %>%
  select(n_unique_tokens, n_non_stop_unique_tokens) %>%
  filter(n_unique_tokens > 0.5 & n_non_stop_unique_tokens > 0.7)
```

### 3
```{r}
library(tidyr)

# This will gather all the 'data_channel' columns into key-value pairs
long_data <- my_data %>%
  gather(key = "channel_type", value = "channel_value", starts_with("data_channel"))
# --------------------------------------------------------------

# This will spread the 'channel_type' and 'channel_value' back into separate columns
wide_data <- long_data %>%
  spread(key = "channel_type", value = "channel_value")
# --------------------------------------------------------------

# This will unite 'weekday_is_monday' to 'weekday_is_sunday' into a new column 'weekdays_combined'
united_data <- my_data %>%
  unite("weekdays_combined", weekday_is_monday:weekday_is_sunday, sep = ",")
# --------------------------------------------------------------------------

# This nests the data frame by 'num_keywords', storing the nested 'data' in a new column
nested_data <- my_data %>%
  nest(data = c(n_tokens_title, n_tokens_content, num_keywords))
```

# Part 2: Reflection and questions on readings

## 1

Design is the third component in the life cycle od software
development.Use design to understand the larger problem you are working
with.

## 2

1.  principle1: Our highest priority is to satisfy the customer through
    early and continuous delivery of valuable software.

Example: I am working on an e-commerce platform. Instead of waiting for
six months to a year to release a complete, feature-packed application,
the team adopts an Agile approach.They prioritize building the most
essential features first, such as user registration and item listings,
and release it to a select group of users for testing within the first
few weeks.

2.  welcome changing requirements even late in development. Agile
    processes harness change for the customer's competitive advantage.

Example: I am building a health monitoring app that tracks physical
activities, sleep, and dietary habits. Three months into development, a
new type of wearable device gains popularity, and the client wants to
incorporate compatibility with this device. In a non-Agile model,
accommodating this new requirement could be problematic, costly, and
time-consuming. However, in an Agile framework, the team would welcome
this change.

## 3

1.  Color-coded Map Markers Mark: The points on the U.S. map in the
    center of the visualization represent golf courses. Channel: Color
    (green for public courses, brown for private courses)

Benefits: The use of color helps viewers instantly differentiate between
public and private courses without having to refer to a legend or click
on each point for details. Colors are easy to understand and don't add
visual clutter to the map.

2.  Line Charts for Rankings Mark: Lines connecting bubbles on the
    chart. Channel: Position on a vertical axis (for rankings), and a
    horizontal axis (for years). The colors of the lines correspond to
    the upper-right filters for the magazines' rankings.

Benefits: Line charts are excellent for showing trends over time. The
ranking of a course across various years can be easily interpreted.

# Reference

Name(s) of all authors: Keiichiro Watanabe, Megan Bernacchi

Lab: Lab Journal 2

Due Monday, 11 September 2023

Written/online sources used: (enter "none" if no sources other than the
textbook and course website used) : none

Help obtained (Acknowledgments): none

"I/we confirm that the above list of sources is complete AND that I/we
have not talked to anyone else about the solution to this problem."
